---
title: "Control Flow"
output: html_notebook
---

We can control the flow with if, switch() (choice), for and while (loop)

## IF

If returns a value so we can assign value
```{r}
x1 <- if (TRUE) 1 else 2
x2 <- if (FALSE) 2
x1
x2
```
Example for the value of if can assign value
```{r}
greet <- function(name, birthday = FALSE) {
  paste0(
    "Hi ", name, 
    if (birthday) " and happy Bday")
}

greet("Minh", TRUE)
```

## SWITCH
Switch can help to reduce the if function like this
```{r}
x_option <- function(x) {
  if (x == "a") {
    "option 1"
  } else if (x == "b") {
    "option 2" 
  } else if (x == "c") {
    "option 3"
  } else {
    stop("Invalid `x` value")
  }
}
```
with the more succinct:
```{r}
x_option_sw <- function(x) {
  switch(x,
         a = "option 1", 
         b = "option 2",
         c = "option 3", 
         stop = ("Invalid `x` value"))
}
```

```{r}
x_option_sw("100")
```

Switch can be used with numeric but if x is not a whole number, undesirable output would happen. Therefore it is recommended that using switch to character input only.

Exercise: what is the output?
```{r}
ifelse(TRUE, 1, "no")
```
the function ifelse has the description like this ifelse(test, yes, no). 

Exercise: why the following code work?
```{r}
x <- 1:10
y <- numeric()
empty_check <- function(x) {if (length(x)) "Not empty" else "Empty"}
empty_check(x)
empty_check(y)
```

## LOOPS
example of loops
```{r}
for (i in 1:3) {print(i)}
```
NOTE: for assign the item for that specific variable name, and overwrite all the previous name
```{r}
i <- 100
for (i in 1:3) {}
i
```
There are a few way to terminate loop early: next (exit the current iteration) or break (exit the entire for loop)

example
```{r}
for (i in 1:10000) {
  if (i <3) 
    next
  print(i)
  
  if (i>=6)
    break
}
```

```{r}
means <- c(1, 50, 20)
out <- vector("list", length(means))
for (i in 1:length(means)) {
  out[[i]] <- rnorm(10, means[[i]])
}
```



