---
title: "Vectors"
output:
  pdf_document: default
  html_notebook: default
---
## Types of Vectors
In this chapter, I would learn about the type of vectors. There are basically 4 types of vectors. That is logical (TRUE- FALSE), Integer (non decimal values, NaN and Inf, -Inf), Double (decimal values) and Character.

Vector that is the same type of elements is Atomic Vector. Otherwise it is a list.
```{r}
lgl_var <- c(TRUE, FALSE)
int_var <- c(1L, 6L, 10L)
dbl_var <- c(1, 2.5, 4.5)
chr_var <- c("these are", "some strings")
```

To get the type of the vector, we would use the function typeof()

```{r}
typeof(lgl_var)
typeof(int_var)
typeof(dbl_var)
typeof(chr_var)
```
## Missing values
Calculation with NA are mostly NA. Excepting some cases

```{r}
NA + 10
NA *10
NA < 10
!NA
```

NA is something between TRUE and FALSE. Let's see it. When doing with TRUE and FALSE, | returns in TRUE & returns in FALSE. NA is in between.
```{r}
NA| TRUE
NA & TRUE
NA | FALSE
NA & FALSE
```
```{r}
NA ^ 0
```
Checking if NA equal NA or other numbers. Returns all in NA.

```{r}
x <- c(NA, 1, NA, 2)
x == NA
```

## Testing and Coercion

We can use the function is.*() to test the type of a vector. But it applies to is.logical(), is.integer(), is.double() and is.character()

```{r}
is.logical(lgl_var)
is.integer(lgl_var)
is.double(dbl_var)
is.character(chr_var)
```
Check carefully if you use these tests below by reading their documentation:
```{r}
is.vector(lgl_var)
is.numeric(chr_var)
is.atomic(dbl_var)
```

